### 2012-11-15 ASA2013/asa2013.tex
la2pdf commit - 2012:11:15	14:32:28	(Thu15.Nov)
la2pdf commit - 2012:11:15	16:40:44	(Thu15.Nov)

\begin{abstract}
The MVDR adaptive beamformer has lately been shown to improve image quality in active sonar systems, but at a major computational expense. This is because the estimation and inversion of a spatial covariance matrix is required for each image pixel. We target this problem by altering and mapping the MVDR algorithm GPU, and suggest three different solutions depending on the system size.

For systems with less than 32 channels, we suggest arithmetic optimizations for the estimation step, and show how a careful mapping to a high-end GPU to yield processing rates of more than 1\,Mpx/s. When the system exceeds this size, we show that frequency domain processing can be employed instead, which allows a comparable performance to be maintained, at a neglible reduction in image quality. These GPU implementations consistently reduced the runtime by 2-3 orders of magnitude compared to our reference C and Matlab implementations.

>>>>

\begin{abstract}
The MVDR adaptive beamformer has lately been shown to improve image quality in active sonar systems, but at a major computational expense. This is because the estimation and inversion of a spatial covariance matrix is required for each image pixel. We target this problem by altering and mapping the MVDR algorithm to a GPU, and suggest three different solutions depending on the system size.

For systems with less than 32 channels, we suggest arithmetic optimizations for the estimation step, and show how a GPU can be used to yield processing rates of more than 1\,Mpx/s. When the system exceeds this size, we show that frequency domain processing can be employed, which allows a comparable performance to be maintained, at a neglible reduction in image quality. These GPU implementations consistently reduced the runtime by 2-3 orders of magnitude compared to our reference C and Matlab implementations.
